---
title: Non verbal communication dogs - Dwell time analysis
author: Lucrezia Lonardo
date: 09/02/2025
output: html_document
---
notes: 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(tidyverse)
library(dplyr)
library(ggplot2)
library(glmmTMB)
library(ggpubr)
#library(ggpubr)
#library(grid)
#library(summarytools)
#library(exactRankTests)
#library(car)
#library(lme4)
# source("./functions/diagnostic_fcns.r")
# source("./functions/glmm_stability.r")
# source("./functions/boot_glmm.r")
# source("./functions/boot_glmm2.r")
# source("./functions/glmmTMB_stability.r")
# source("./functions/boot_glmmTMB.r")
# source("./functions/extract_ranef_gmmTMB.r")
```

### Import data - video IP 

```{r}
#IA report (whole video IP)
video.ip.orig.data <- read_delim("data/IA_report_new_video_IP.txt", na=".", delim="\t") %>% 
  filter(RECORDING_SESSION_LABEL!="Nala_2",
         RECORDING_SESSION_LABEL!="Sahibu_2",
         RECORDING_SESSION_LABEL!="Melody_1") #sessions repeated due to dog leaving chinrest too soon (before reaction of reacting agent)
levels(as.factor(video.ip.orig.data$IA_LABEL))

#demographic data
demo.data <- read_csv("data/Non_verbal_communication_counterbalancing.csv")%>%
  mutate(EDF3=fct_recode(as.factor(EDF3), "Georgia_3"="Georgia3", "Mathilda_3"="Mathild3"))%>%
  separate(EDF3, c("subject", "num"), sep="_") %>% 
  select(-num) %>% 
  filter(!is.na(subject))

#full data file (IA report + demographics)
video.ip.data <- video.ip.orig.data %>%
  select(RECORDING_SESSION_LABEL, IP_LABEL, IA_LABEL,IA_ID, Trial_Index_, condition, trial_type, session_number, trial_number, video_file, DATA_FILE,  IA_AREA, IA_AVERAGE_FIX_PUPIL_SIZE,  IA_DWELL_TIME, "IA_DWELL_TIME_%", IA_FIXATION_COUNT, IA_MAX_FIX_PUPIL_SIZE, INTEREST_AREA_FIXATION_SEQUENCE, TRIAL_DWELL_TIME, TRIAL_FIXATION_COUNT, TRIAL_IA_COUNT, TRIAL_TOTAL_VISITED_IA_COUNT, IA_FIRST_FIXATION_TIME )%>%
  mutate(RECORDING_SESSION_LABEL=fct_recode(RECORDING_SESSION_LABEL, Georgia_1="Georgia1",Georgia_2="Georgia2", Georgia_3="Georgia3",Georgia_4="Georgia4", Mathilda_1="Mathild1", Mathilda_2="Mathild2", Mathilda_3="Mathild3", Mathilda_4="Mathild4" ))%>%
  separate(RECORDING_SESSION_LABEL, c("subject", "session.num"), sep = "_") %>% 
  full_join(demo.data)
```

###Data checks (whole video IP)

```{r}
dwell.descr <-video.ip.data %>%
  filter(IA_LABEL!="FIXATION_TRIGGER") %>% 
  group_by(subject, trial_number, condition, trial_type, IA_LABEL, TRIAL_DWELL_TIME) %>% 
  summarise(ia_dwell_time=IA_DWELL_TIME) %>% 
   mutate(agent_type = ifelse(grepl("inviting|pointing", IA_LABEL), 
                             "communicating", 
                             "reacting")) %>% 
  mutate(proportion.dwell.time.agents=ia_dwell_time/TRIAL_DWELL_TIME)
  
xx=table(dwell.descr$condition, dwell.descr$subject)
ncol(xx) #39 dogs were tested
xx #each dog should have 2 trials per condition (1 fam, 1 test)
colSums(xx < 2) #2 dogs have 3 (CA, CG and GA) and 1 (GA) missing sessions, 
#but they are still included in the final sample

#in case one wants to exclude these 2 dogs who did not complete all sessions due to 
#owner dropping out:
# dwell.descr<-dwell.descr %>% 
#   filter(subject != "Lenny" & subject != "Floki")
# 
# xx=table(dwell.descr$condition, dwell.descr$subject)
# colSums(xx < 2) #no dogs with missing sessions left 
```

### Descriptive stats (whole video IP)
```{r}
#descriptive statistics
dwell.descr.aggr<-dwell.descr %>% 
  group_by(condition, trial_type) %>% 
  summarise(mean_dwell_time_to_agents=mean(ia_dwell_time),
            median_dwell_time=median(ia_dwell_time),
            mean_prop_dwell_agents=mean(proportion.dwell.time.agents, na.rm = TRUE),
            sd_dwell= sd(ia_dwell_time, na.rm = TRUE),
            se_dwell=sd(ia_dwell_time, na.rm = TRUE)/sqrt(length(ia_dwell_time)))

dwell.descr.part<-dwell.descr %>% 
  group_by(condition, subject) %>% 
  summarise(mean_dwell_time_to_agents=mean(ia_dwell_time, na.rm = TRUE),
            median_dwell_time=median(ia_dwell_time),
            mean_prop_dwell_agents=mean(proportion.dwell.time.agents, na.rm = TRUE),
            sd_dwell= sd(ia_dwell_time, na.rm = TRUE),
            se_dwell=sd(ia_dwell_time, na.rm = TRUE)/sqrt(length(ia_dwell_time)))
```

### Bring data into right format for dwell time analysis (whole video)
```{r}
dwell.time.data<-video.ip.data %>% 
  filter(IA_LABEL!="FIXATION_TRIGGER") %>% 
  group_by(subject, trial_number, condition, trial_type) %>% 
  summarise(dwell_time_to_agents=sum(IA_DWELL_TIME))
```
###Plot dwell times (whole video)

```{r}
#Version 1 (2 boxplots, one for congruent, one for incongruent conditions)
dwell.descr$trial_type<-fct_recode(dwell.descr$trial_type, "Congruent"="cong", "Incongruent"="incong")
ggplot(data = dwell.descr.part, aes(x = trial_type, y = ia_dwell_time)) +
  geom_boxplot(alpha = 0.5) +  # Boxplot with transparency
  geom_jitter(aes(fill = condition),  # Jitter points and color by condition
              position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
              alpha = 0.5, shape = 21) +  # Add transparency and shape
  ylab("Dwell time") +
  xlab("Condition") +
  #ylim(2500, 15000) +  
  theme_bw()+
  stat_compare_means(paired = TRUE, method = "t.test", label.x= 1.4, label.y = 1300 )

t.test(dwell.descr.part$mean_dwell_time_to_agents[dwell.descr.part$condition=="CA"], dwell.descr.part$mean_dwell_time_to_agents[dwell.descr.part$condition=="CG"], paired=TRUE)
#LL:It seems there is no difference in the dwell times to the 2 agents combined. Next, do the same for the acting agent alone (or the 2 agents separately)
```


```{r}
# #Version 1.1 (with grouped subjects observations)
# ggplot(data = dwell.descr, aes(x = trial_type, y = ia_dwell_time)) +
#   geom_boxplot(alpha = 0.5) +  # Boxplot with transparency
#   geom_jitter(aes(fill = condition),  # Jitter points and color by condition
#               position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
#               alpha = 0.5, shape = 21) +  # Add transparency and shape
#   # Add lines connecting observations for CA-CG and GG-GA
#   geom_line(
#     data = dwell.descr[dwell.descr$condition %in% c("CA", "CG"), ], 
#     aes(group = subject), 
#     position = position_dodge(width = 0.75), 
#     color = "blue", alpha = 0.7, linewidth = 0.5
#   ) +
#   geom_line(
#     data = dwell.descr[dwell.descr$condition %in% c("GG", "GA"), ], 
#     aes(group = subject), 
#     position = position_dodge(width = 0.75), 
#     color = "red", alpha = 0.7, linewidth = 0.5
#   ) +
#   ylab("Dwell time") +
#   xlab("Condition") +
#   ylim(2500, 15000) +  
#   theme_bw()
# 
# 
# 
# 
# #Version 2
# ggplot(data = dwell.descr, aes(x = condition, y = ia_dwell_time, fill = condition)) +
#   geom_boxplot(alpha = 0.3, color = "black") +  # Boxplot with lower transparency and black borders
#   geom_jitter(aes(color = condition),  # Jitter points with color by condition
#               position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
#               alpha = 0.6, shape = 21) +  # Slightly less transparent points
#   ylab("Dwell time (ms)") +
#   xlab("Condition") +
#   ylim(2500, 15000) +  
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 0, hjust = 1),  # Possibly rotate x-axis labels for readability
#         panel.grid.major.x = element_blank()) +
#   scale_x_discrete(labels = function(x) {  # Custom x-axis labels to include trial_type values
#     # Replace with your actual labels for trial_type and condition, if needed
#     paste(x, "(Trial Type: X)", sep = "\n")
#   }) +
#   guides(fill = "none")  # Remove redundant fill legend
# 
# 
# #Version 3
# 
# 
# # Reorder levels of condition
# dwell.descr$condition <- factor(dwell.descr$condition, levels = c("CA", "CG", "GG", "GA"))
# 
# # Plot
# ggplot(data = dwell.descr, aes(x = condition, y = ia_dwell_time, fill = condition)) +
#   geom_boxplot(alpha = 0.3, color = "black") +  # Boxplots with lower transparency
#   geom_jitter(aes(color = condition),  # Jitter points with color by condition
#               position = position_jitterdodge(jitter.width = 0.4, dodge.width = 0.75), 
#               alpha = 0.6, shape = 21) +  # Points with less transparency
#   ylab("Dwell time (ms)") +
#   xlab("Condition") +  
#  # ylim(2500, 15000) +  
#   theme_bw() +
#   theme(
#     axis.text.x = element_text(size = 10),  # Keep axis labels unrotated
#     panel.grid.major.x = element_blank(),
#     axis.ticks.length = unit(0.5, "cm"),
#     plot.margin = margin(t = 10, r = 10, b = 50, l = 10)  # Add space below plot
#   ) +
#   scale_x_discrete(
#     labels = c("CA", "CG", "GG", "GA")  # Custom order of conditions
#   ) +
#   guides(fill = "none", color = "none") +  # Remove redundant legends
#   # Add custom labels below the x-axis
#   annotate(
#     "text", x = 1.5, y = -2450, label = "Congruent", size = 5, hjust = 0.5, vjust = 1, fontface = "bold"
#   ) +
#   annotate(
#     "text", x = 3.5, y = -2450, label = "Incongruent", size = 5, hjust = 0.5, vjust = 1, fontface = "bold"
#   )
# 
# 
# 
# 
# library(ggplot2)
# library(grid)
# 
# 
# # Reorder levels of condition
# dwell.descr$condition <- factor(dwell.descr$condition, levels = c("CA", "CG", "GG", "GA"))
# 
# # Base ggplot
# p <- ggplot(data = dwell.descr, aes(x = condition, y = ia_dwell_time, fill = condition)) +
#   geom_boxplot(alpha = 0.3, color = "black") +  # Boxplots with lower transparency
#   geom_jitter(aes(color = condition),  # Jitter points with color by condition
#               position = position_jitterdodge(jitter.width = 0.4, dodge.width = 0.75), 
#               alpha = 0.6, shape = 21) +  # Points with less transparency
#   ylab("Dwell time (ms)") +
#   xlab("Condition") +  
#   #ylim(2500, 15000) +  
#   theme_bw() +
#   theme(
#     axis.text.x = element_text(size = 10),  # Keep axis labels unrotated
#     panel.grid.major.x = element_blank(),
#     axis.ticks.length = unit(0.5, "cm"),
#     plot.margin = margin(t = 10, r = 10, b = 60, l = 10)  # Add space below plot
#   ) +
#   scale_x_discrete(
#     labels = c("CA", "CG", "GG", "GA")  # Custom order of conditions
#   ) +
#   guides(fill = "none", color = "none")  # Remove redundant legends
# 
# # Print the ggplot and add grid text
# print(p)
# 
# # Add external labels
# grid.text("Congruent", x = 0.3, y = -1, gp = gpar(fontsize = 10, fontface = "bold"))
# grid.text("Incongruent", x = 0.7, y = -1, gp = gpar(fontsize = 10, fontface = "bold"))
# 
# p
```

* T-test comparing dwell times between object congruent and incongruent IAs
```{r}
test.IP.end.data.object.congruent.hand<-test.IP.end.data.object.congruent%>%
  filter(condition=="hand")

t.test(test.IP.end.data.object.congruent.hand$mean_dwell[test.IP.end.data.object.congruent.hand$object_congruent=="object_congruent_dwell_time"], test.IP.end.data.object.congruent.hand$mean_dwell[test.IP.end.data.object.congruent.hand$object_congruent=="object_incongruent_dwell_time"], paired=TRUE)
```


## Import data - reaction IP - duration: the last 13200 ms (does not contain info about familiarisation anymore)

```{r}
#IA report (from reaction IP - from frame 579 for Zserbo - session 1)
reaction.ip.orig.data.Zserbo <- read_delim("data/IA_report_IP_from_reaction_frame579.txt", na=".", delim="\t") %>% 
   filter(RECORDING_SESSION_LABEL=="Zserbo_1")

#IA report (from reaction IP - from frame 580 for all other sessions)
reaction.ip.orig.data <- read_delim("data/IA_report_IP_from_reaction.txt", na=".", delim="\t") %>% 
  filter(RECORDING_SESSION_LABEL!="Nala_2",
         RECORDING_SESSION_LABEL!="Sahibu_2",
         RECORDING_SESSION_LABEL!="Melody_1", #until here repeated due to dog leaving chinrest too early (before second agent's reaction)
         RECORDING_SESSION_LABEL!="Zserbo_1") %>% #excluded from here because frame 580 (the one defining the beginning of the reaction IP) was skipped in this video presentation, so we import this trial from frame 579 below
  rbind(reaction.ip.orig.data.Zserbo) %>% 
  arrange(RECORDING_SESSION_LABEL) #order rows alphabetically based on RECORDING_SESSION_LABEL
  levels(as.factor(reaction.ip.orig.data$IA_LABEL))

#demographic data
demo.data <- read_csv("data/Non_verbal_communication_counterbalancing.csv")%>%
  mutate(EDF3=fct_recode(as.factor(EDF3), "Georgia_3"="Georgia3", "Mathilda_3"="Mathild3"))%>%
  separate(EDF3, c("subject", "num"), sep="_") %>% 
  select(-num) %>% 
  filter(!is.na(subject))
 
#full data file (IA report_IP_from reaction + demographics)
reaction.ip.data <- reaction.ip.orig.data %>%
  select(RECORDING_SESSION_LABEL, IP_LABEL, IA_LABEL,IA_ID, Trial_Index_, condition, trial_type, session_number, trial_number, video_file, DATA_FILE,  IA_AREA, IA_AVERAGE_FIX_PUPIL_SIZE,  IA_DWELL_TIME, "IA_DWELL_TIME_%", IA_FIXATION_COUNT, IA_MAX_FIX_PUPIL_SIZE, INTEREST_AREA_FIXATION_SEQUENCE, TRIAL_DWELL_TIME, TRIAL_FIXATION_COUNT, TRIAL_IA_COUNT, TRIAL_TOTAL_VISITED_IA_COUNT, IA_FIRST_FIXATION_TIME )%>%
  mutate(RECORDING_SESSION_LABEL=fct_recode(RECORDING_SESSION_LABEL, Georgia_1="Georgia1",Georgia_2="Georgia2", Georgia_3="Georgia3",Georgia_4="Georgia4", Mathilda_1="Mathild1", Mathilda_2="Mathild2", Mathilda_3="Mathild3", Mathilda_4="Mathild4" ))%>%
  separate(RECORDING_SESSION_LABEL, c("subject", "session.num"), sep = "_") %>% 
  full_join(demo.data)

#data checks
summary(reaction.ip.data$TRIAL_DWELL_TIME)
which(is.na(reaction.ip.data$TRIAL_DWELL_TIME)) #Knopf --> not sure what this is (no data, not even in the viewing session)
levels(as.factor(reaction.ip.data$subject))
```

###Descriptive stats (reaction IP)

```{r}
#descriptive statistics

dwell.descr.react <-reaction.ip.data %>%
  filter(IA_LABEL!="FIXATION_TRIGGER") %>% 
  group_by(subject, trial_number, condition, trial_type, IA_LABEL, TRIAL_DWELL_TIME) %>% 
  summarise(ia_dwell_time=IA_DWELL_TIME) %>% 
   mutate(agent_type = ifelse(grepl("inviting|pointing", IA_LABEL), 
                             "communicating", 
                             "reacting")) %>% 
  mutate(proportion.dwell.time.agents=ia_dwell_time/TRIAL_DWELL_TIME) %>% 
  ungroup()

dwell.descr.aggr.react<-dwell.descr.react %>% 
  group_by(condition, trial_type) %>% 
  summarise(mean_dwell_time_to_agents=mean(ia_dwell_time),
            median_dwell_time=median(ia_dwell_time),
            mean_prop_dwell_agents=mean(proportion.dwell.time.agents, na.rm = TRUE),
            sd_dwell= sd(ia_dwell_time, na.rm = TRUE),
            se_dwell=sd(ia_dwell_time, na.rm = TRUE)/sqrt(length(ia_dwell_time)))

dwell.descr.part.react<-dwell.descr.react %>% 
  group_by(condition, subject) %>% 
  summarise(mean_dwell_time_to_agents=mean(ia_dwell_time, na.rm = TRUE),
            median_dwell_time=median(ia_dwell_time),
            mean_prop_dwell_agents=mean(proportion.dwell.time.agents, na.rm = TRUE),
            sd_dwell= sd(ia_dwell_time, na.rm = TRUE),
            se_dwell=sd(ia_dwell_time, na.rm = TRUE)/sqrt(length(ia_dwell_time)))
```
###Checking the data
```{r}
table(dwell.descr.part.react$condition, dwell.descr.part.react$subject) 

xx=table(dwell.descr.part.react$condition, dwell.descr.part.react$subject)
ncol(xx) #39 dogs were tested
xx #each dog should have 1 test trial per condition
sum(colSums(xx < 1)) #some dogs have missing sessions
colSums(xx < 1) #2 dogs have 3 (CA, CG and GA) and 1 (GA) missing sessions, 
#but they are still included in the final sample

#in case one wants to exclude these 2 dogs
# dwell.descr.react.wo.excl.dogs<-dwell.descr.react %>% 
#   filter(subject!="Lenny" & subject!="Floki")
```
###Plot dwell times as a function of trial type (based on aggregated data)

```{r}
#Version 1 (2 boxplots, one for congruent, one for incongruent conditions)
dwell.descr.aggr.react$trial_type<-fct_recode(dwell.descr.aggr.react$trial_type, "Congruent"="cong", "Incongruent"="incong")

ggplot(data = dwell.descr.aggr.react, aes(x = trial_type, y = mean_dwell_time_to_agents)) +
  geom_boxplot(alpha = 0.5) +  # Boxplot with transparency
  #geom_jitter(aes(fill = condition),  # Jitter points and color by condition
              # position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
              # alpha = 0.5, shape = 21) +  # Add transparency and shape
  ylab("Mean dwell time to agents") +
  xlab("Trial type") +
  ylim(3850, 4500) +  
  theme_bw()+
  stat_compare_means(paired = TRUE, method = "t.test", label.x= 1.4, label.y = 4500 )

```
### Plot showing also condition, based on trial by trial data
```{r}
ggplot(data = dwell.descr.react, 
       aes(x = interaction(agent_type, trial_type, sep = "\n"), 
           y = ia_dwell_time)) +
  geom_boxplot(alpha = 0.5) +  # Boxplot with transparency
  # geom_jitter(aes(fill = condition),  # Uncomment to add jittered points colored by condition
  #             position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
  #             alpha = 0.5, shape = 21) +  # Add transparency and shape
  ylab("Mean dwell time to agents") +
  xlab("Agent Type\nTrial Type") +  # Label for clarity
  #ylim(3850, 4500) +  
  theme_bw()

#t-test to check if dogs looked longer at the reacting than communicating agent
#aggregate data to get one average value per participant and agent type:
dwell.descr.react.grouped<-dwell.descr.react %>% 
  group_by(subject, agent_type) %>% 
  summarise(mean_dwell_time=mean(ia_dwell_time),
            sd_dwell_time=sd(ia_dwell_time))
  
t.test(dwell.descr.react.grouped$mean_dwell_time[dwell.descr.react.grouped$agent_type=="reacting"], dwell.descr.react.grouped$mean_dwell_time[dwell.descr.react.grouped$agent_type=="communicating"], paired=T) #seems so
```

###Preparing the data for analysis

```{r}
#bringing the data in the right format
model.data<-dwell.descr.react  %>%
  select(-IA_LABEL, -ia_dwell_time) %>% 
 pivot_wider(names_from=agent_type, values_from = proportion.dwell.time.agents) %>% 
  rename(prop.dwellt.communicating.agent=communicating, 
         prop.dwellt.reacting.agent=reacting)

summary(model.data$prop.dwellt.communicating.agent)
summary(model.data$prop.dwellt.reacting.agent)

#transforming DV to exclude 0 and 1s
model.data$prop.dwellt.communicating.agent.scaled <-
  (model.data$prop.dwellt.communicating.agent *
      (length(model.data$prop.dwellt.communicating.agent) - 1) + 0.5) / length(model.data$prop.dwellt.communicating.agent)

model.data$prop.dwellt.reacting.agent.scaled <-
  (model.data$prop.dwellt.reacting.agent *
      (length(model.data$prop.dwellt.reacting.agent) - 1) + 0.5) / length(model.data$prop.dwellt.reacting.agent)

summary(model.data$prop.dwellt.communicating.agent.scaled)
summary(model.data$prop.dwellt.reacting.agent.scaled)


model.data <- data.frame(model.data) %>%
  mutate(
    z.trial = as.numeric(scale(as.numeric(trial_number), center = TRUE, scale = TRUE)), #z-transform trial number
    condition.c = as.numeric(scale(as.numeric(as.factor(condition)), center = TRUE, scale = FALSE)),
    trial_type.c = as.numeric(scale(as.numeric(as.factor(trial_type)), center = TRUE, scale = FALSE))
  ) %>% #manually dummy code and center condition and trial_type for random effects part of the model
#the first as.numeric in this code is needed to drop the [,1] specification add would automatically add to the column names otherwise
  mutate(condition=as.factor(condition),
         trial_type=as.factor(trial_type)) #ensure condition and trial_type as treated as factors

hist(model.data$prop.dwellt.communicating.agent.scaled)
hist(model.data$prop.dwellt.reacting.agent.scaled)
```
### Descriptive stats 2 - separated by agents in the reaction IP

```{r}
dwell.descr.react.each.agent<-model.data %>% 
  group_by(condition, trial_type) %>% 
  summarise(mean_prop_dwell_time_communicating=mean(prop.dwellt.communicating.agent),
            mean_prop_dwell_time_reacting=mean(prop.dwellt.reacting.agent),
            sd_prop_dwell_comm=sd(prop.dwellt.communicating.agent, na.rm = TRUE),
            sd_prop_dwell_comm=sd(prop.dwellt.communicating.agent, na.rm = TRUE),
            median_dwell_timecomm=median(prop.dwellt.communicating.agent),
            median_dwell_time_react=median(prop.dwellt.reacting.agent),
            se_prop_dwell_comunicating=sd(prop.dwellt.communicating.agent, na.rm = TRUE)/sqrt(length(prop.dwellt.communicating.agent)),
            se_prop_dwell_reacting=sd(prop.dwellt.reacting.agent, na.rm = TRUE)/sqrt(length(prop.dwellt.reacting.agent)))
```

#### Beta GLMM -reaction IP

```{r}
#models for communicating agent (one with trial_type and one with condition as dv)
m1.reactIP.comm.trial.type<-glmmTMB(prop.dwellt.communicating.agent.scaled ~ trial_type + z.trial + (1+trial_type.c+z.trial||subject), family=beta_family, data=model.data,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))
#correlation between random effects excluded due to convergence issues

m2.reactIP.comm.cond<-glmmTMB(prop.dwellt.communicating.agent.scaled ~ condition + z.trial + (1+condition.c+z.trial||subject), family=beta_family, data=model.data,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))
#correlation between random effects excluded due to convergence issues

#models for reacting agent (one with trial_type and one with condition as dv)
m1.reactIP.react.trial.type<-glmmTMB(prop.dwellt.reacting.agent.scaled ~ trial_type + z.trial + (1+trial_type.c+z.trial||subject), family=beta_family, data=model.data,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))
#correlation between random effects excluded due to convergence issues

m2.reactIP.react.cond<-glmmTMB(prop.dwellt.reacting.agent.scaled ~ condition + z.trial + (1+condition.c+z.trial||subject), family=beta_family, data=model.data,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))
#correlation between random effects excluded due to convergence issues

#LL: missing: fit reduced models without condition to assess the significance of condition as a whole

#evaluate results
round(summary(m1.reactIP.comm.trial.type)$coefficients$cond,2)
round(summary(m2.reactIP.comm.cond)$coefficients$cond,2)
round(summary(m1.reactIP.react.trial.type)$coefficients$cond,2)
round(summary(m2.reactIP.react.cond)$coefficients$cond,2)#here conditionCG is (barely) significant: dogs look less long at the reacting agent in the CG (inc) than in the CA (cong) condition

#LL: next, fit on the data in dwell.decr.react a beta model with interaction to check if dogs look longer to one of the agents or the other depending on the condition ia_dwell_time ~ condition (and/or trial_type)* agent_type




```


