---
title: Non verbal communication dogs - Dwell time analysis
author: Lucrezia Lonardo
date: 18/11/2024
output: html_document
---
notes: 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(tidyverse)
library(dplyr)
library(ggplot2)
library(grid)
#library(summarytools)
#library(exactRankTests)
library(ggpubr)
#library(glmmTMB)
#library(car)
#library(lme4)
# source("./functions/diagnostic_fcns.r")
# source("./functions/glmm_stability.r")
# source("./functions/boot_glmm.r")
# source("./functions/boot_glmm2.r")
# source("./functions/glmmTMB_stability.r")
# source("./functions/boot_glmmTMB.r")
# source("./functions/extract_ranef_gmmTMB.r")
```

### Import data - video IP

```{r}
#IA report
video.ip.orig.data <- read_delim("data/IA_report.txt", na=".", delim="\t")
levels(as.factor(video.ip.orig.data$IA_LABEL))

#demographic data
demo.data <- read_csv("data/Non_verbal_communication_counterbalancing.csv")%>%
  mutate(EDF3=fct_recode(as.factor(EDF3), "Georgia_3"="Georgia3", "Mathilda_3"="Mathild3"))%>%
  separate(EDF3, c("subject", "num"), sep="_") %>% 
  select(-num) %>% 
  filter(!is.na(subject))

#full data
video.ip.data <- video.ip.orig.data %>%
  select(RECORDING_SESSION_LABEL, IP_LABEL, IA_LABEL,IA_ID, Trial_Index_, condition, trial_type, session_number, trial_number, video_file, DATA_FILE,  IA_AREA, IA_AVERAGE_FIX_PUPIL_SIZE,  IA_DWELL_TIME, "IA_DWELL_TIME_%", IA_FIXATION_COUNT, IA_MAX_FIX_PUPIL_SIZE, INTEREST_AREA_FIXATION_SEQUENCE, TRIAL_DWELL_TIME, TRIAL_FIXATION_COUNT, TRIAL_IA_COUNT, TRIAL_TOTAL_VISITED_IA_COUNT, IA_FIRST_FIXATION_TIME )%>%
  mutate(RECORDING_SESSION_LABEL=fct_recode(RECORDING_SESSION_LABEL, Georgia_1="Georgia1",Georgia_2="Georgia2", Georgia_3="Georgia3",Georgia_4="Georgia4", Mathilda_1="Mathild1", Mathilda_2="Mathild2", Mathilda_3="Mathild3", Mathilda_4="Mathild4" ))%>%
  separate(RECORDING_SESSION_LABEL, c("subject", "session.num"), sep = "_") %>% 
  full_join(demo.data)
```


###Descriptive stats

```{r}
#descriptive statistics
dwell.descr <-video.ip.data %>%
  filter(IA_LABEL!="FIXATION_TRIGGER") %>% 
  group_by(subject, trial_number, condition, trial_type, IA_LABEL, TRIAL_DWELL_TIME) %>% 
  summarise(ia_dwell_time=IA_DWELL_TIME) %>% 
   mutate(agent_type = ifelse(grepl("inviting|pointing", IA_LABEL), 
                             "communicating", 
                             "reacting")) %>% 
  mutate(proportion.dwell.time.agents=ia_dwell_time/TRIAL_DWELL_TIME)
  

dwell.descr.aggr<-dwell.descr %>% 
  group_by(condition, trial_type) %>% 
  summarise(mean_dwell_time_to_agents=mean(ia_dwell_time),
            median_dwell_time=median(ia_dwell_time),
            mean_prop_dwell_agents=mean(proportion.dwell.time.agents, na.rm = TRUE),
            sd_dwell= sd(ia_dwell_time, na.rm = TRUE),
            se_dwell=sd(ia_dwell_time, na.rm = TRUE)/sqrt(length(ia_dwell_time)))

dwell.descr.part<-dwell.descr %>% 
  group_by(condition, subject) %>% 
  summarise(mean_dwell_time_to_agents=mean(ia_dwell_time, na.rm = TRUE),
            median_dwell_time=median(ia_dwell_time),
            mean_prop_dwell_agents=mean(proportion.dwell.time.agents, na.rm = TRUE),
            sd_dwell= sd(ia_dwell_time, na.rm = TRUE),
            se_dwell=sd(ia_dwell_time, na.rm = TRUE)/sqrt(length(ia_dwell_time)))
```
###Checking the data
```{r}
table(dwell.descr.part$condition, dwell.descr.part$subject) #Mailo misses 1 observation in CA, so for now I exclude him
dwell.descr.part<-dwell.descr.part %>% 
  filter(subject!="Mailo")
```
### Bring data into right format for dwell time analysis
```{r}
dwell.time.data<-video.ip.data %>% 
  filter(IA_LABEL!="FIXATION_TRIGGER") %>% 
  group_by(subject, trial_number, condition, trial_type) %>% 
  summarise(dwell_time_to_agents=sum(IA_DWELL_TIME))
```
###Plot dwell times

```{r}
#Version 1 (2 boxplots, one for congruent, one for incongruent conditions)
dwell.descr$trial_type<-fct_recode(dwell.descr$trial_type, "Congruent"="cong", "Incongruent"="incong")
ggplot(data = dwell.descr.part, aes(x = trial_type, y = ia_dwell_time)) +
  geom_boxplot(alpha = 0.5) +  # Boxplot with transparency
  geom_jitter(aes(fill = condition),  # Jitter points and color by condition
              position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
              alpha = 0.5, shape = 21) +  # Add transparency and shape
  ylab("Dwell time") +
  xlab("Condition") +
  #ylim(2500, 15000) +  
  theme_bw()+
  stat_compare_means(paired = TRUE, method = "t.test", label.x= 1.4, label.y = 1300 )

t.test(dwell.descr.part$mean_dwell_time_to_agents[dwell.descr.part$condition=="CA"], dwell.descr.part$mean_dwell_time_to_agents[dwell.descr.part$condition=="CG"], paired=TRUE)
#LL:It seems there is no difference in the dwell times to the 2 agents combined. Next, do the same for the acting agent alone (or the 2 agents separately)
```


```{r}
# #Version 1.1 (with grouped subjects observations)
# ggplot(data = dwell.descr, aes(x = trial_type, y = ia_dwell_time)) +
#   geom_boxplot(alpha = 0.5) +  # Boxplot with transparency
#   geom_jitter(aes(fill = condition),  # Jitter points and color by condition
#               position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
#               alpha = 0.5, shape = 21) +  # Add transparency and shape
#   # Add lines connecting observations for CA-CG and GG-GA
#   geom_line(
#     data = dwell.descr[dwell.descr$condition %in% c("CA", "CG"), ], 
#     aes(group = subject), 
#     position = position_dodge(width = 0.75), 
#     color = "blue", alpha = 0.7, linewidth = 0.5
#   ) +
#   geom_line(
#     data = dwell.descr[dwell.descr$condition %in% c("GG", "GA"), ], 
#     aes(group = subject), 
#     position = position_dodge(width = 0.75), 
#     color = "red", alpha = 0.7, linewidth = 0.5
#   ) +
#   ylab("Dwell time") +
#   xlab("Condition") +
#   ylim(2500, 15000) +  
#   theme_bw()
# 
# 
# 
# 
# #Version 2
# ggplot(data = dwell.descr, aes(x = condition, y = ia_dwell_time, fill = condition)) +
#   geom_boxplot(alpha = 0.3, color = "black") +  # Boxplot with lower transparency and black borders
#   geom_jitter(aes(color = condition),  # Jitter points with color by condition
#               position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
#               alpha = 0.6, shape = 21) +  # Slightly less transparent points
#   ylab("Dwell time (ms)") +
#   xlab("Condition") +
#   ylim(2500, 15000) +  
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 0, hjust = 1),  # Possibly rotate x-axis labels for readability
#         panel.grid.major.x = element_blank()) +
#   scale_x_discrete(labels = function(x) {  # Custom x-axis labels to include trial_type values
#     # Replace with your actual labels for trial_type and condition, if needed
#     paste(x, "(Trial Type: X)", sep = "\n")
#   }) +
#   guides(fill = "none")  # Remove redundant fill legend
# 
# 
# #Version 3
# 
# 
# # Reorder levels of condition
# dwell.descr$condition <- factor(dwell.descr$condition, levels = c("CA", "CG", "GG", "GA"))
# 
# # Plot
# ggplot(data = dwell.descr, aes(x = condition, y = ia_dwell_time, fill = condition)) +
#   geom_boxplot(alpha = 0.3, color = "black") +  # Boxplots with lower transparency
#   geom_jitter(aes(color = condition),  # Jitter points with color by condition
#               position = position_jitterdodge(jitter.width = 0.4, dodge.width = 0.75), 
#               alpha = 0.6, shape = 21) +  # Points with less transparency
#   ylab("Dwell time (ms)") +
#   xlab("Condition") +  
#  # ylim(2500, 15000) +  
#   theme_bw() +
#   theme(
#     axis.text.x = element_text(size = 10),  # Keep axis labels unrotated
#     panel.grid.major.x = element_blank(),
#     axis.ticks.length = unit(0.5, "cm"),
#     plot.margin = margin(t = 10, r = 10, b = 50, l = 10)  # Add space below plot
#   ) +
#   scale_x_discrete(
#     labels = c("CA", "CG", "GG", "GA")  # Custom order of conditions
#   ) +
#   guides(fill = "none", color = "none") +  # Remove redundant legends
#   # Add custom labels below the x-axis
#   annotate(
#     "text", x = 1.5, y = -2450, label = "Congruent", size = 5, hjust = 0.5, vjust = 1, fontface = "bold"
#   ) +
#   annotate(
#     "text", x = 3.5, y = -2450, label = "Incongruent", size = 5, hjust = 0.5, vjust = 1, fontface = "bold"
#   )
# 
# 
# 
# 
# library(ggplot2)
# library(grid)
# 
# 
# # Reorder levels of condition
# dwell.descr$condition <- factor(dwell.descr$condition, levels = c("CA", "CG", "GG", "GA"))
# 
# # Base ggplot
# p <- ggplot(data = dwell.descr, aes(x = condition, y = ia_dwell_time, fill = condition)) +
#   geom_boxplot(alpha = 0.3, color = "black") +  # Boxplots with lower transparency
#   geom_jitter(aes(color = condition),  # Jitter points with color by condition
#               position = position_jitterdodge(jitter.width = 0.4, dodge.width = 0.75), 
#               alpha = 0.6, shape = 21) +  # Points with less transparency
#   ylab("Dwell time (ms)") +
#   xlab("Condition") +  
#   #ylim(2500, 15000) +  
#   theme_bw() +
#   theme(
#     axis.text.x = element_text(size = 10),  # Keep axis labels unrotated
#     panel.grid.major.x = element_blank(),
#     axis.ticks.length = unit(0.5, "cm"),
#     plot.margin = margin(t = 10, r = 10, b = 60, l = 10)  # Add space below plot
#   ) +
#   scale_x_discrete(
#     labels = c("CA", "CG", "GG", "GA")  # Custom order of conditions
#   ) +
#   guides(fill = "none", color = "none")  # Remove redundant legends
# 
# # Print the ggplot and add grid text
# print(p)
# 
# # Add external labels
# grid.text("Congruent", x = 0.3, y = -1, gp = gpar(fontsize = 10, fontface = "bold"))
# grid.text("Incongruent", x = 0.7, y = -1, gp = gpar(fontsize = 10, fontface = "bold"))
# 
# p
```

* T-test comparing dwell times between object congruent and incongruent IAs
```{r}
test.IP.end.data.object.congruent.hand<-test.IP.end.data.object.congruent%>%
  filter(condition=="hand")

t.test(test.IP.end.data.object.congruent.hand$mean_dwell[test.IP.end.data.object.congruent.hand$object_congruent=="object_congruent_dwell_time"], test.IP.end.data.object.congruent.hand$mean_dwell[test.IP.end.data.object.congruent.hand$object_congruent=="object_incongruent_dwell_time"], paired=TRUE)
```


#### Beta GLMM

```{r}

model.data.end.IP.largerIA<-end.ip.data.wider%>%
  filter(object_congruent=="object_congruent_dwell_time")%>%
  mutate(z.trial=scale(trial_within_block, center = TRUE, scale=TRUE), # trial within condition
         condition.c=scale(as.numeric(as.factor(condition)), center = TRUE, scale=FALSE))

summary(model.data.end.IP.largerIA)
```

```{r}
model.data.end.IP.largerIA$prop.dwell.scaled <-
  (
    model.data.end.IP.largerIA$proportion.object.congruent.dwell.time_noNA *
      (
        length(
          model.data.end.IP.largerIA$proportion.object.congruent.dwell.time_noNA
        ) - 1
      ) + 0.5
  ) / length(model.data.end.IP.largerIA$proportion.object.congruent.dwell.time_noNA)#transform DV to exclude 0 and 1s

m1.endIP.largeIA<-glmmTMB(prop.dwell.scaled ~ condition + z.trial + condition_first +  target_location+(1+condition.c+z.trial||subject), family=beta_family, data=model.data.end.IP.largerIA,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

summary(m1.endIP.largeIA)
round(summary(m1.endIP.largeIA)$coefficients$cond,2)
```


```{r}
drop1_m1<-drop1(m1.endIP.largeIA, test="Chisq")
round(drop1_m1,3)
```

```{r}


m2.endIP.largeIA<-glmmTMB(prop.dwell.scaled ~ condition*target_location+z.trial +(1+condition.c+z.trial||subject), family=beta_family, data=model.data.end.IP.largerIA,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

```

```{r}
drop1_m2<-drop1(m2.endIP.largeIA, test="Chisq")
drop1_m2
```
##### assumptions
```{r}
#overdispersion
overdisp.test(m1.endIP.largeIA)

#distribution of the BLUPs
ranef.diagn.plot(m1.endIP.largeIA) 

#collinearity
xx=lme4::lmer(prop.dwell.scaled ~ condition + z.trial + condition_first +  target_location +
(1+condition.c+z.trial||subject),
data=model.data.end.IP.largerIA)
round(vif(xx), 3)
```

##### model stability beta model prop. dwell time
```{r}
m1.endIP.largeIA.stab=glmmTMB.stab(model.res=m1.endIP.largeIA, para=F, data=model.data.end.IP.largerIA)

#stability table
round(m1.endIP.largeIA.stab$summary[1:5, -1],2)
#stability plot
m.stab.plot(round(m1.endIP.largeIA.stab$summary[1:5, -1], 3))
```

##### confidence intervals beta model prop. dwell time
```{r}
boot.m1.endIP.largeIA=boot.glmmtmb(m=m1.endIP.largeIA, data=model.data.end.IP.largerIA,
discard.non.conv=F, nboots=1000, para=T, resol=100,
level=0.95, n.cores="all-1")

round(boot.m1.endIP.largeIA$ci.estimates$fe[1:5,],2)
```


The results of the dwell time analysis of the end IP show no difference between the hand or claw condition with respect to the looking times to the grasped object. Dogs showed a preference to look at the old identity object when this was in the upper location (evidenced by a significant target location effect).

### Intercept only model for proportion congruent object dwell time
```{r}
model.data.end.IP.largerIA$prop.dwell.scaled2 <-
  (
    model.data.end.IP.largerIA$proportion.object.congruent.dwell.time *
      (
        length(
          model.data.end.IP.largerIA$proportion.object.congruent.dwell.time
        ) - 1
      ) + 0.5
  ) / length(model.data.end.IP.largerIA$proportion.object.congruent.dwell.time)#transform DV to exclude 0 and 1s

m1.endIP.largeIA_interceptonly<-glmmTMB(prop.dwell.scaled2 ~  z.trial+(1+z.trial||subject), family=beta_family, data=model.data.end.IP.largerIA,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

round(summary(m1.endIP.largeIA_interceptonly)$coefficients$cond,3)
```

### First fixation analysis (binary)
```{r}
model.data.end.IP.first.looks<-end.ip.first.look%>%
  mutate(z.trial=scale(trial_within_block, center = TRUE, scale=TRUE),
         condition.c=scale(as.numeric(as.factor(condition)), center = TRUE, scale=FALSE))

summary(model.data.end.IP.first.looks)


m1.endIP.first_look<-glmer(object_congruent_first_look_noNA ~ condition + z.trial + condition_first+ target_location+(1+condition.c+z.trial|subject), family=binomial, data=model.data.end.IP.first.looks, control=glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000000)))

round(summary(m1.endIP.first_look)$coefficients,2)
```


```{r}
drop1_m1.first.look<-drop1(m1.endIP.first_look, test="Chisq")
round(drop1_m1.first.look,3)
```
####assumptions and stability
```{r}
#BLUPs
ranef.diagn.plot(m1.endIP.first_look)

#Stability
stab.m1.endIP.first_look=glmm.model.stab(model.res=m1.endIP.first_look,
contr=glmerControl(optimizer="bobyqa",
optCtrl=list(maxfun=10000)))

round(stab.m1.endIP.first_look$summary[1:5, -1],2)
m.stab.plot(stab.m1.endIP.first_look$summary[, -1])
```
####CIs binomial model first fixation
```{r}
boot.m1.endIP.first_look=boot.glmm.pred(model.res=m1.endIP.first_look,
nboots=1000, para=T, resol=1000, level=0.95,
use=NULL, n.cores="all-1")

first.fix.bin.cis<-round(boot.m1.endIP.first_look$ci.estimates, 2)
first.fix.bin.cis
```


### Intercept only model for first look
```{r}
m1.endIP.first_look_interceptonly<-glmer(object_congruent_first_look ~ 1+z.trial+(1+z.trial|subject), family=binomial, data=model.data.end.IP.first.looks, control=glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000000)))

round(summary(m1.endIP.first_look_interceptonly)$coefficients,3)
```

###First fixation to incongruent object (binary model)
```{r}
end.ip.first.look.incongr <- end.ip.data %>%
  select(
    subject,
    session.num,
    condition_trial,
    IP_LABEL,
    IA_LABEL,
    condition,
    condition_first,
    target,
    target_location,
    session,
    trial_within_block,
    video_file,
    video_latency,
    DATA_FILE,
    IA_FIRST_FIXATION_TIME
  ) %>%
  pivot_wider(names_from = IA_LABEL, values_from = IA_FIRST_FIXATION_TIME) %>%
  mutate(
    upper_IA_large = as.numeric(upper_IA_large),
    lower_IA_large = as.numeric(lower_IA_large)
  ) %>% 
 mutate(first_look = ifelse((
    upper_IA_large < lower_IA_large |
      (!is.na(upper_IA_large) & is.na(lower_IA_large))
  ), "upper", "NA")) %>%
  mutate(first_look2 = ifelse((
    lower_IA_large < upper_IA_large |
      (!is.na(lower_IA_large) & is.na(upper_IA_large))
  ), "lower", "NA")) %>% 

  mutate(first_look3=coalesce(first_look, first_look2)) %>% 
  mutate(object_incongruent_first_look = as.numeric(ifelse((target_location ==
                                                            "up" &
                                                            first_look3 == "lower"),
                                                         0,
                                                         ifelse((target_location == "down" &
                                                                   first_look3 == "upper"),
                                                                0,
                                                                ifelse((target_location == "up" &
                                                                          first_look3 == "upper"),
                                                                       1,
                                                                       ifelse((
                                                                         target_location == "down" & first_look3 == "lower"
                                                                       ), 1, NA)
                                                                )
                                                         )
  )),
  object_incongruent_first_look_noNA = as.numeric(ifelse(is.na(first_look3),0, object_incongruent_first_look )))

summary(end.ip.first.look.incongr$object_incongruent_first_look_noNA)

#manually replacing Nas that were not automatically scored correctly
end.ip.first.look.incongr[c(67,97),"object_incongruent_first_look_noNA"] <-0
 
summary(end.ip.first.look.incongr$object_incongruent_first_look_noNA)
```

```{r}
model.data.end.IP.first.look.incongr<-end.ip.first.look.incongr%>%
  mutate(z.trial=scale(trial_within_block, center = TRUE, scale=TRUE),
         condition.c=scale(as.numeric(as.factor(condition)), center = TRUE, scale=FALSE))

summary(model.data.end.IP.first.look.incongr)


m1.endIP.first_look.incongr<-glmer(object_incongruent_first_look_noNA ~ condition + z.trial + condition_first+ target_location+(1+condition.c+z.trial|subject), family=binomial, data=model.data.end.IP.first.look.incongr, control=glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000000)))

round(summary(m1.endIP.first_look.incongr)$coefficients,2)
```

```{r}
drop1_m1.first.look.incongr<-drop1(m1.endIP.first_look.incongr, test="Chisq")
round(drop1_m1.first.look.incongr,3)
```
####assumptions and stability first fix incongr obj
```{r}
#BLUPs
ranef.diagn.plot(m1.endIP.first_look.incongr)

#Stability
stab.m1.endIP.first_look.incongr=glmm.model.stab(model.res=m1.endIP.first_look.incongr,
contr=glmerControl(optimizer="bobyqa",
optCtrl=list(maxfun=10000)))

round(stab.m1.endIP.first_look.incongr$summary[1:5, -1],2)
m.stab.plot(stab.m1.endIP.first_look.incongr$summary[, -1])
```
####CIs binomial model first fixation incongr obj
```{r}
boot.m1.endIP.first_look.incongr=boot.glmm.pred(model.res=m1.endIP.first_look.incongr,
nboots=1000, para=T, resol=1000, level=0.95,
use=NULL, n.cores="all-1")

first.fix.incongr.bin.cis<-round(boot.m1.endIP.first_look.incongr$ci.estimates, 2)
first.fix.incongr.bin.cis
```