---
title: Non verbal communication dogs - Dwell time analysis
author: Lucrezia Lonardo
date: 18/11/2024
output: html_document
---
notes: 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(tidyverse)
library(dplyr)
#library(summarytools)
#library(exactRankTests)
#library(ggpubr)
#library(glmmTMB)
#library(car)
#library(lme4)
# source("./functions/diagnostic_fcns.r")
# source("./functions/glmm_stability.r")
# source("./functions/boot_glmm.r")
# source("./functions/boot_glmm2.r")
# source("./functions/glmmTMB_stability.r")
# source("./functions/boot_glmmTMB.r")
# source("./functions/extract_ranef_gmmTMB.r")
```

### Import data - video IP

```{r}
#IA report
video.ip.orig.data <- read_delim("data/IA_report.txt", na=".", delim="\t")
levels(as.factor(video.ip.orig.data$IA_LABEL))

#demographic data
demo.data <- read_csv("data/Non_verbal_communication_counterbalancing.csv")%>%
  mutate(EDF3=fct_recode(as.factor(EDF3), "Georgia_3"="Georgia3", "Mathilda_3"="Mathild3"))%>%
  separate(EDF3, c("subject", "num"), sep="_") %>% 
  select(-num) %>% 
  filter(!is.na(subject))

#full data
video.ip.data <- video.ip.orig.data %>%
  select(RECORDING_SESSION_LABEL, IP_LABEL, IA_LABEL,IA_ID, Trial_Index_, condition, trial_type, session_number, trial_number, video_file, DATA_FILE,  IA_AREA, IA_AVERAGE_FIX_PUPIL_SIZE,  IA_DWELL_TIME, "IA_DWELL_TIME_%", IA_FIXATION_COUNT, IA_MAX_FIX_PUPIL_SIZE, INTEREST_AREA_FIXATION_SEQUENCE, TRIAL_DWELL_TIME, TRIAL_FIXATION_COUNT, TRIAL_IA_COUNT, TRIAL_TOTAL_VISITED_IA_COUNT, IA_FIRST_FIXATION_TIME )%>%
  mutate(RECORDING_SESSION_LABEL=fct_recode(RECORDING_SESSION_LABEL, Georgia_1="Georgia1",Georgia_2="Georgia2", Georgia_3="Georgia3",Georgia_4="Georgia4", Mathilda_1="Mathild1", Mathilda_2="Mathild2", Mathilda_3="Mathild3", Mathilda_4="Mathild4" ))%>%
  separate(RECORDING_SESSION_LABEL, c("subject", "session.num"), sep = "_") %>% 
  full_join(demo.data)
```

###Descriptive stats

```{r}
#descriptive statistics
dwell.descr <-video.ip.data %>%
  filter(IA_LABEL!="FIXATION_TRIGGER") %>% 
  group_by(subject, trial_number, condition, trial_type, IA_LABEL, TRIAL_DWELL_TIME) %>% 
  summarise(ia_dwell_time=IA_DWELL_TIME) %>% 
   mutate(agent_type = ifelse(grepl("inviting|pointing", IA_LABEL), 
                             "communicating", 
                             "reacting")) %>% 
  mutate(proportion.dwell.time.agents=ia_dwell_time/TRIAL_DWELL_TIME)
  

dwell.descr.aggr<-dwell.descr %>% 
  group_by(condition) %>% 
  summarise(mean_dwell_time_to_agents=mean(ia_dwell_time),
            mean_prop_dwell_agents=mean(proportion.dwell.time.agents, na.rm = TRUE),
            sd_dwell= sd(ia_dwell_time, na.rm = TRUE),
            se_dwell=sd(ia_dwell_time, na.rm = TRUE)/sqrt(length(ia_dwell_time)))
```

### Bring data into right format for dwell time analysis
```{r}
dwell.time.data<-video.ip.data %>% 
  filter(IA_LABEL!="FIXATION_TRIGGER") %>% 
  group_by(subject, trial_number, condition, trial_type) %>% 
  summarise(dwell_time_to_agents=sum(IA_DWELL_TIME))
```
###Plot dwell times

```{r}



ggplot(data = test.IP.end.data%>%filter(condition=="claw"), aes(x=IA_LABEL, y=mean_dwell))+
  geom_boxplot(alpha=0.5)+#, outlier.colour = "white")+
  #geom_point(aes(x=first_target_loc, y=IA_DWELL_TIME, group=IA_LABEL),position_dodge(), alpha=0.5)+
  facet_grid(~target_location)+
  ylab("Dwell time")+xlab("Condition")+
  #ylim(0,3000)+
  theme_bw()+
  stat_compare_means(paired = TRUE, method = "t.test", label.y = 1500 )










#LL from here old Woodward script: 
end.ip.data.wider <- video.ip.data %>%
  select(
    subject,
    session.num,
    condition_trial,
    IP_LABEL,
    IA_LABEL,
    condition,
    condition_first,
    target,
    target_location,
    session,
    trial_within_block,
    video_file,
    video_latency,
    DATA_FILE,
    IA_DWELL_TIME
  ) %>%
  pivot_wider(names_from = IA_LABEL, values_from = IA_DWELL_TIME) %>%
  mutate(
    object_congruent_dwell_time = as.numeric(ifelse(
      target_location == "up",
      lower_IA_large,
      ifelse(target_location == "down", upper_IA_large, "")
    )),
    object_IA_dwell_time = lower_IA_large + upper_IA_large,
    object_incongruent_dwell_time = as.numeric(ifelse(
      target_location == "up",
      upper_IA_large,
      ifelse(target_location == "down", lower_IA_large, "")
    ))
  ) %>%
  select(-lower_IA_large,-upper_IA_large) %>%
  pivot_longer(
    cols = c(object_congruent_dwell_time, object_incongruent_dwell_time),
    names_to = "object_congruent",
    values_to = "dwell_time"
  ) %>%
  mutate(
    proportion.object.congruent.dwell.time = dwell_time / object_IA_dwell_time,
    proportion.object.congruent.dwell.time_noNA = as.numeric(ifelse(
      is.na(proportion.object.congruent.dwell.time),
      0,
      proportion.object.congruent.dwell.time
    )
    ))


end.ip.first.look <- video.ip.data %>%
  select(
    subject,
    session.num,
    condition_trial,
    IP_LABEL,
    IA_LABEL,
    condition,
    condition_first,
    target,
    target_location,
    session,
    trial_within_block,
    video_file,
    video_latency,
    DATA_FILE,
    IA_FIRST_FIXATION_TIME
  ) %>%
  pivot_wider(names_from = IA_LABEL, values_from = IA_FIRST_FIXATION_TIME) %>%
  mutate(
    upper_IA_large = as.numeric(upper_IA_large),
    lower_IA_large = as.numeric(lower_IA_large)
  ) %>%
  mutate(first_look = ifelse((
    upper_IA_large < lower_IA_large |
      (!is.na(upper_IA_large) & is.na(lower_IA_large))
  ), "upper", "")) %>%
  mutate(first_look2 = ifelse((
    lower_IA_large < upper_IA_large |
      (!is.na(lower_IA_large) & is.na(upper_IA_large))
  ), "lower", "")) %>%
  mutate(first_look3 = ifelse(
    !is.na(first_look),
    first_look,
    ifelse(!is.na(first_look2), first_look2, NA)
  )) %>%
  mutate(object_congruent_first_look = as.numeric(ifelse((target_location ==
                                                            "up" &
                                                            first_look3 == "lower"),
                                                         1,
                                                         ifelse((target_location == "down" &
                                                                   first_look3 == "upper"),
                                                                1,
                                                                ifelse((target_location == "up" &
                                                                          first_look3 == "upper"),
                                                                       0,
                                                                       ifelse((
                                                                         target_location == "down" & first_look3 == "lower"
                                                                       ), 0, NA)
                                                                )
                                                         )
  )),
  object_congruent_first_look_noNA = as.numeric(ifelse(is.na(first_look3),0, object_congruent_first_look )))

#manually replacing Nas that were not automatically scored correctly
end.ip.first.look[c(67,97),"object_congruent_first_look_noNA"] <-0

#checks:
view(dfSummary(video.ip.data))

table(video.ip.data$trial_within_block, video.ip.data$subject)
table(video.ip.data$condition, video.ip.data$subject)
table(video.ip.data$session.num, video.ip.data$subject)
table(video.ip.data$condition, video.ip.data$TRIAL_TOTAL_VISITED_IA_COUNT)

```


* Absolute dwell time
```{r}
test.IP.end.data <- end.ip.data %>%
  group_by(subject, condition, target_location, IA_LABEL)%>%
  summarise(mean_dwell=mean(IA_DWELL_TIME))



ggplot(data = test.IP.end.data%>%filter(condition=="hand"), aes(x=IA_LABEL, y=mean_dwell))+
  geom_boxplot(alpha=0.5)+#, outlier.colour = "white")+
  #geom_point(aes(x=first_target_loc, y=IA_DWELL_TIME, group=IA_LABEL),position_dodge(), alpha=0.5)+
  facet_grid(~target_location)+
  ylab("Dwell time")+xlab("Condition")+
  #ylim(0,3000)+
  theme_bw()+
  stat_compare_means(paired = TRUE, method = "t.test", label.y = 1500 )

```
* Proportion dwell time
```{r}


test.IP.end.data.object.congruent <- end.ip.data.wider %>%
  group_by(subject, condition, object_congruent)%>%
  summarise(mean_dwell=mean(dwell_time), mean_proportion_dwell=mean(proportion.object.congruent.dwell.time, na.rm = TRUE))



ggplot(data = test.IP.end.data.object.congruent, aes(x=object_congruent, y=mean_dwell))+
  geom_boxplot(alpha=0.5)+#, outlier.colour = "white")+
  geom_point(alpha=0.3)+
  geom_line(aes(group=subject), alpha=0.3)+
  facet_wrap(~condition)+
  ylab("Dwell time")+xlab("Object congruency")+
  #ylim(0,3000)+
  theme_bw()+
  stat_compare_means(paired = TRUE, method = "t.test", label.y = 1500 )


ggplot(data = test.IP.end.data.object.congruent, aes(x=object_congruent, y=mean_proportion_dwell))+
  geom_boxplot(alpha=0.5)+#, outlier.colour = "white")+
  geom_point(alpha=0.3)+
  geom_line(aes(group=subject), alpha=0.3)+
  facet_wrap(~condition)+
  ylab("Proportion dwell time")+xlab("Object congruency")+
  #ylim(0,3000)+
  theme_bw()+
  stat_compare_means(paired = TRUE, method = "t.test", label.y = 0.8 )
```

* T-test comparing dwell times between object congruent and incongruent IAs
```{r}
test.IP.end.data.object.congruent.hand<-test.IP.end.data.object.congruent%>%
  filter(condition=="hand")

t.test(test.IP.end.data.object.congruent.hand$mean_dwell[test.IP.end.data.object.congruent.hand$object_congruent=="object_congruent_dwell_time"], test.IP.end.data.object.congruent.hand$mean_dwell[test.IP.end.data.object.congruent.hand$object_congruent=="object_incongruent_dwell_time"], paired=TRUE)
```


#### Beta GLMM

```{r}

model.data.end.IP.largerIA<-end.ip.data.wider%>%
  filter(object_congruent=="object_congruent_dwell_time")%>%
  mutate(z.trial=scale(trial_within_block, center = TRUE, scale=TRUE), # trial within condition
         condition.c=scale(as.numeric(as.factor(condition)), center = TRUE, scale=FALSE))

summary(model.data.end.IP.largerIA)
```

```{r}
model.data.end.IP.largerIA$prop.dwell.scaled <-
  (
    model.data.end.IP.largerIA$proportion.object.congruent.dwell.time_noNA *
      (
        length(
          model.data.end.IP.largerIA$proportion.object.congruent.dwell.time_noNA
        ) - 1
      ) + 0.5
  ) / length(model.data.end.IP.largerIA$proportion.object.congruent.dwell.time_noNA)#transform DV to exclude 0 and 1s

m1.endIP.largeIA<-glmmTMB(prop.dwell.scaled ~ condition + z.trial + condition_first +  target_location+(1+condition.c+z.trial||subject), family=beta_family, data=model.data.end.IP.largerIA,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

summary(m1.endIP.largeIA)
round(summary(m1.endIP.largeIA)$coefficients$cond,2)
```


```{r}
drop1_m1<-drop1(m1.endIP.largeIA, test="Chisq")
round(drop1_m1,3)
```

```{r}


m2.endIP.largeIA<-glmmTMB(prop.dwell.scaled ~ condition*target_location+z.trial +(1+condition.c+z.trial||subject), family=beta_family, data=model.data.end.IP.largerIA,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

```

```{r}
drop1_m2<-drop1(m2.endIP.largeIA, test="Chisq")
drop1_m2
```
##### assumptions
```{r}
#overdispersion
overdisp.test(m1.endIP.largeIA)

#distribution of the BLUPs
ranef.diagn.plot(m1.endIP.largeIA) 

#collinearity
xx=lme4::lmer(prop.dwell.scaled ~ condition + z.trial + condition_first +  target_location +
(1+condition.c+z.trial||subject),
data=model.data.end.IP.largerIA)
round(vif(xx), 3)
```

##### model stability beta model prop. dwell time
```{r}
m1.endIP.largeIA.stab=glmmTMB.stab(model.res=m1.endIP.largeIA, para=F, data=model.data.end.IP.largerIA)

#stability table
round(m1.endIP.largeIA.stab$summary[1:5, -1],2)
#stability plot
m.stab.plot(round(m1.endIP.largeIA.stab$summary[1:5, -1], 3))
```

##### confidence intervals beta model prop. dwell time
```{r}
boot.m1.endIP.largeIA=boot.glmmtmb(m=m1.endIP.largeIA, data=model.data.end.IP.largerIA,
discard.non.conv=F, nboots=1000, para=T, resol=100,
level=0.95, n.cores="all-1")

round(boot.m1.endIP.largeIA$ci.estimates$fe[1:5,],2)
```


The results of the dwell time analysis of the end IP show no difference between the hand or claw condition with respect to the looking times to the grasped object. Dogs showed a preference to look at the old identity object when this was in the upper location (evidenced by a significant target location effect).

### Intercept only model for proportion congruent object dwell time
```{r}
model.data.end.IP.largerIA$prop.dwell.scaled2 <-
  (
    model.data.end.IP.largerIA$proportion.object.congruent.dwell.time *
      (
        length(
          model.data.end.IP.largerIA$proportion.object.congruent.dwell.time
        ) - 1
      ) + 0.5
  ) / length(model.data.end.IP.largerIA$proportion.object.congruent.dwell.time)#transform DV to exclude 0 and 1s

m1.endIP.largeIA_interceptonly<-glmmTMB(prop.dwell.scaled2 ~  z.trial+(1+z.trial||subject), family=beta_family, data=model.data.end.IP.largerIA,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

round(summary(m1.endIP.largeIA_interceptonly)$coefficients$cond,3)
```

### First fixation analysis (binary)
```{r}
model.data.end.IP.first.looks<-end.ip.first.look%>%
  mutate(z.trial=scale(trial_within_block, center = TRUE, scale=TRUE),
         condition.c=scale(as.numeric(as.factor(condition)), center = TRUE, scale=FALSE))

summary(model.data.end.IP.first.looks)


m1.endIP.first_look<-glmer(object_congruent_first_look_noNA ~ condition + z.trial + condition_first+ target_location+(1+condition.c+z.trial|subject), family=binomial, data=model.data.end.IP.first.looks, control=glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000000)))

round(summary(m1.endIP.first_look)$coefficients,2)
```


```{r}
drop1_m1.first.look<-drop1(m1.endIP.first_look, test="Chisq")
round(drop1_m1.first.look,3)
```
####assumptions and stability
```{r}
#BLUPs
ranef.diagn.plot(m1.endIP.first_look)

#Stability
stab.m1.endIP.first_look=glmm.model.stab(model.res=m1.endIP.first_look,
contr=glmerControl(optimizer="bobyqa",
optCtrl=list(maxfun=10000)))

round(stab.m1.endIP.first_look$summary[1:5, -1],2)
m.stab.plot(stab.m1.endIP.first_look$summary[, -1])
```
####CIs binomial model first fixation
```{r}
boot.m1.endIP.first_look=boot.glmm.pred(model.res=m1.endIP.first_look,
nboots=1000, para=T, resol=1000, level=0.95,
use=NULL, n.cores="all-1")

first.fix.bin.cis<-round(boot.m1.endIP.first_look$ci.estimates, 2)
first.fix.bin.cis
```


### Intercept only model for first look
```{r}
m1.endIP.first_look_interceptonly<-glmer(object_congruent_first_look ~ 1+z.trial+(1+z.trial|subject), family=binomial, data=model.data.end.IP.first.looks, control=glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000000)))

round(summary(m1.endIP.first_look_interceptonly)$coefficients,3)
```

###First fixation to incongruent object (binary model)
```{r}
end.ip.first.look.incongr <- end.ip.data %>%
  select(
    subject,
    session.num,
    condition_trial,
    IP_LABEL,
    IA_LABEL,
    condition,
    condition_first,
    target,
    target_location,
    session,
    trial_within_block,
    video_file,
    video_latency,
    DATA_FILE,
    IA_FIRST_FIXATION_TIME
  ) %>%
  pivot_wider(names_from = IA_LABEL, values_from = IA_FIRST_FIXATION_TIME) %>%
  mutate(
    upper_IA_large = as.numeric(upper_IA_large),
    lower_IA_large = as.numeric(lower_IA_large)
  ) %>% 
 mutate(first_look = ifelse((
    upper_IA_large < lower_IA_large |
      (!is.na(upper_IA_large) & is.na(lower_IA_large))
  ), "upper", "NA")) %>%
  mutate(first_look2 = ifelse((
    lower_IA_large < upper_IA_large |
      (!is.na(lower_IA_large) & is.na(upper_IA_large))
  ), "lower", "NA")) %>% 

  mutate(first_look3=coalesce(first_look, first_look2)) %>% 
  mutate(object_incongruent_first_look = as.numeric(ifelse((target_location ==
                                                            "up" &
                                                            first_look3 == "lower"),
                                                         0,
                                                         ifelse((target_location == "down" &
                                                                   first_look3 == "upper"),
                                                                0,
                                                                ifelse((target_location == "up" &
                                                                          first_look3 == "upper"),
                                                                       1,
                                                                       ifelse((
                                                                         target_location == "down" & first_look3 == "lower"
                                                                       ), 1, NA)
                                                                )
                                                         )
  )),
  object_incongruent_first_look_noNA = as.numeric(ifelse(is.na(first_look3),0, object_incongruent_first_look )))

summary(end.ip.first.look.incongr$object_incongruent_first_look_noNA)

#manually replacing Nas that were not automatically scored correctly
end.ip.first.look.incongr[c(67,97),"object_incongruent_first_look_noNA"] <-0
 
summary(end.ip.first.look.incongr$object_incongruent_first_look_noNA)
```

```{r}
model.data.end.IP.first.look.incongr<-end.ip.first.look.incongr%>%
  mutate(z.trial=scale(trial_within_block, center = TRUE, scale=TRUE),
         condition.c=scale(as.numeric(as.factor(condition)), center = TRUE, scale=FALSE))

summary(model.data.end.IP.first.look.incongr)


m1.endIP.first_look.incongr<-glmer(object_incongruent_first_look_noNA ~ condition + z.trial + condition_first+ target_location+(1+condition.c+z.trial|subject), family=binomial, data=model.data.end.IP.first.look.incongr, control=glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000000)))

round(summary(m1.endIP.first_look.incongr)$coefficients,2)
```

```{r}
drop1_m1.first.look.incongr<-drop1(m1.endIP.first_look.incongr, test="Chisq")
round(drop1_m1.first.look.incongr,3)
```
####assumptions and stability first fix incongr obj
```{r}
#BLUPs
ranef.diagn.plot(m1.endIP.first_look.incongr)

#Stability
stab.m1.endIP.first_look.incongr=glmm.model.stab(model.res=m1.endIP.first_look.incongr,
contr=glmerControl(optimizer="bobyqa",
optCtrl=list(maxfun=10000)))

round(stab.m1.endIP.first_look.incongr$summary[1:5, -1],2)
m.stab.plot(stab.m1.endIP.first_look.incongr$summary[, -1])
```
####CIs binomial model first fixation incongr obj
```{r}
boot.m1.endIP.first_look.incongr=boot.glmm.pred(model.res=m1.endIP.first_look.incongr,
nboots=1000, para=T, resol=1000, level=0.95,
use=NULL, n.cores="all-1")

first.fix.incongr.bin.cis<-round(boot.m1.endIP.first_look.incongr$ci.estimates, 2)
first.fix.incongr.bin.cis
```