---
title: Non verbal communication dogs - Dwell time analysis
author: Lucrezia Lonardo
date: 18/11/2024
output: html_document
---
notes: 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(tidyverse)
library(dplyr)
library(ggplot2)
library(glmmTMB)
library(ggpubr)
#library(ggpubr)
#library(grid)
#library(summarytools)
#library(exactRankTests)
#library(car)
#library(lme4)
# source("./functions/diagnostic_fcns.r")
# source("./functions/glmm_stability.r")
# source("./functions/boot_glmm.r")
# source("./functions/boot_glmm2.r")
# source("./functions/glmmTMB_stability.r")
# source("./functions/boot_glmmTMB.r")
# source("./functions/extract_ranef_gmmTMB.r")
```

### Import data - video IP LL: check afterwads if this (whole video IP) was needed 

```{r}
#IA report (whole video IP)
video.ip.orig.data <- read_delim("data/IA_report.txt", na=".", delim="\t") %>% 
  filter(RECORDING_SESSION_LABEL!="Nala_2",
         RECORDING_SESSION_LABEL!="Sahibu_2",
         RECORDING_SESSION_LABEL!="Melody_1") #sessions repeated due to do leaving chinrest too soon (before reaction of reacting agent)
levels(as.factor(video.ip.orig.data$IA_LABEL))

#demographic data
demo.data <- read_csv("data/Non_verbal_communication_counterbalancing.csv")%>%
  mutate(EDF3=fct_recode(as.factor(EDF3), "Georgia_3"="Georgia3", "Mathilda_3"="Mathild3"))%>%
  separate(EDF3, c("subject", "num"), sep="_") %>% 
  select(-num) %>% 
  filter(!is.na(subject))

#full data file (IA report + demographics)
video.ip.data <- video.ip.orig.data %>%
  select(RECORDING_SESSION_LABEL, IP_LABEL, IA_LABEL,IA_ID, Trial_Index_, condition, trial_type, session_number, trial_number, video_file, DATA_FILE,  IA_AREA, IA_AVERAGE_FIX_PUPIL_SIZE,  IA_DWELL_TIME, "IA_DWELL_TIME_%", IA_FIXATION_COUNT, IA_MAX_FIX_PUPIL_SIZE, INTEREST_AREA_FIXATION_SEQUENCE, TRIAL_DWELL_TIME, TRIAL_FIXATION_COUNT, TRIAL_IA_COUNT, TRIAL_TOTAL_VISITED_IA_COUNT, IA_FIRST_FIXATION_TIME )%>%
  mutate(RECORDING_SESSION_LABEL=fct_recode(RECORDING_SESSION_LABEL, Georgia_1="Georgia1",Georgia_2="Georgia2", Georgia_3="Georgia3",Georgia_4="Georgia4", Mathilda_1="Mathild1", Mathilda_2="Mathild2", Mathilda_3="Mathild3", Mathilda_4="Mathild4" ))%>%
  separate(RECORDING_SESSION_LABEL, c("subject", "session.num"), sep = "_") %>% 
  full_join(demo.data)
```

###Descriptive stats (whole video IP)

```{r}
#descriptive statistics
dwell.descr <-video.ip.data %>%
  filter(IA_LABEL!="FIXATION_TRIGGER") %>% 
  group_by(subject, trial_number, condition, trial_type, IA_LABEL, TRIAL_DWELL_TIME) %>% 
  summarise(ia_dwell_time=IA_DWELL_TIME) %>% 
   mutate(agent_type = ifelse(grepl("inviting|pointing", IA_LABEL), 
                             "communicating", 
                             "reacting")) %>% 
  mutate(proportion.dwell.time.agents=ia_dwell_time/TRIAL_DWELL_TIME)
  

dwell.descr.aggr<-dwell.descr %>% 
  group_by(condition, trial_type) %>% 
  summarise(mean_dwell_time_to_agents=mean(ia_dwell_time),
            median_dwell_time=median(ia_dwell_time),
            mean_prop_dwell_agents=mean(proportion.dwell.time.agents, na.rm = TRUE),
            sd_dwell= sd(ia_dwell_time, na.rm = TRUE),
            se_dwell=sd(ia_dwell_time, na.rm = TRUE)/sqrt(length(ia_dwell_time)))

dwell.descr.part<-dwell.descr %>% 
  group_by(condition, subject) %>% 
  summarise(mean_dwell_time_to_agents=mean(ia_dwell_time, na.rm = TRUE),
            median_dwell_time=median(ia_dwell_time),
            mean_prop_dwell_agents=mean(proportion.dwell.time.agents, na.rm = TRUE),
            sd_dwell= sd(ia_dwell_time, na.rm = TRUE),
            se_dwell=sd(ia_dwell_time, na.rm = TRUE)/sqrt(length(ia_dwell_time)))
```
###Checking the data
```{r}
table(dwell.descr.part$condition, dwell.descr.part$subject) #Mailo misses 1 observation in CA, so for now I exclude him (hopefully he will be tested again)
dwell.descr.part<-dwell.descr.part %>% 
  filter(subject!="Mailo")
```
### Bring data into right format for dwell time analysis
```{r}
dwell.time.data<-video.ip.data %>% 
  filter(IA_LABEL!="FIXATION_TRIGGER") %>% 
  group_by(subject, trial_number, condition, trial_type) %>% 
  summarise(dwell_time_to_agents=sum(IA_DWELL_TIME))
```
###Plot dwell times

```{r}
#Version 1 (2 boxplots, one for congruent, one for incongruent conditions)
dwell.descr$trial_type<-fct_recode(dwell.descr$trial_type, "Congruent"="cong", "Incongruent"="incong")
ggplot(data = dwell.descr.part, aes(x = trial_type, y = ia_dwell_time)) +
  geom_boxplot(alpha = 0.5) +  # Boxplot with transparency
  geom_jitter(aes(fill = condition),  # Jitter points and color by condition
              position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
              alpha = 0.5, shape = 21) +  # Add transparency and shape
  ylab("Dwell time") +
  xlab("Condition") +
  #ylim(2500, 15000) +  
  theme_bw()+
  stat_compare_means(paired = TRUE, method = "t.test", label.x= 1.4, label.y = 1300 )

t.test(dwell.descr.part$mean_dwell_time_to_agents[dwell.descr.part$condition=="CA"], dwell.descr.part$mean_dwell_time_to_agents[dwell.descr.part$condition=="CG"], paired=TRUE)
#LL:It seems there is no difference in the dwell times to the 2 agents combined. Next, do the same for the acting agent alone (or the 2 agents separately)
```


```{r}
# #Version 1.1 (with grouped subjects observations)
# ggplot(data = dwell.descr, aes(x = trial_type, y = ia_dwell_time)) +
#   geom_boxplot(alpha = 0.5) +  # Boxplot with transparency
#   geom_jitter(aes(fill = condition),  # Jitter points and color by condition
#               position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
#               alpha = 0.5, shape = 21) +  # Add transparency and shape
#   # Add lines connecting observations for CA-CG and GG-GA
#   geom_line(
#     data = dwell.descr[dwell.descr$condition %in% c("CA", "CG"), ], 
#     aes(group = subject), 
#     position = position_dodge(width = 0.75), 
#     color = "blue", alpha = 0.7, linewidth = 0.5
#   ) +
#   geom_line(
#     data = dwell.descr[dwell.descr$condition %in% c("GG", "GA"), ], 
#     aes(group = subject), 
#     position = position_dodge(width = 0.75), 
#     color = "red", alpha = 0.7, linewidth = 0.5
#   ) +
#   ylab("Dwell time") +
#   xlab("Condition") +
#   ylim(2500, 15000) +  
#   theme_bw()
# 
# 
# 
# 
# #Version 2
# ggplot(data = dwell.descr, aes(x = condition, y = ia_dwell_time, fill = condition)) +
#   geom_boxplot(alpha = 0.3, color = "black") +  # Boxplot with lower transparency and black borders
#   geom_jitter(aes(color = condition),  # Jitter points with color by condition
#               position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
#               alpha = 0.6, shape = 21) +  # Slightly less transparent points
#   ylab("Dwell time (ms)") +
#   xlab("Condition") +
#   ylim(2500, 15000) +  
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = 0, hjust = 1),  # Possibly rotate x-axis labels for readability
#         panel.grid.major.x = element_blank()) +
#   scale_x_discrete(labels = function(x) {  # Custom x-axis labels to include trial_type values
#     # Replace with your actual labels for trial_type and condition, if needed
#     paste(x, "(Trial Type: X)", sep = "\n")
#   }) +
#   guides(fill = "none")  # Remove redundant fill legend
# 
# 
# #Version 3
# 
# 
# # Reorder levels of condition
# dwell.descr$condition <- factor(dwell.descr$condition, levels = c("CA", "CG", "GG", "GA"))
# 
# # Plot
# ggplot(data = dwell.descr, aes(x = condition, y = ia_dwell_time, fill = condition)) +
#   geom_boxplot(alpha = 0.3, color = "black") +  # Boxplots with lower transparency
#   geom_jitter(aes(color = condition),  # Jitter points with color by condition
#               position = position_jitterdodge(jitter.width = 0.4, dodge.width = 0.75), 
#               alpha = 0.6, shape = 21) +  # Points with less transparency
#   ylab("Dwell time (ms)") +
#   xlab("Condition") +  
#  # ylim(2500, 15000) +  
#   theme_bw() +
#   theme(
#     axis.text.x = element_text(size = 10),  # Keep axis labels unrotated
#     panel.grid.major.x = element_blank(),
#     axis.ticks.length = unit(0.5, "cm"),
#     plot.margin = margin(t = 10, r = 10, b = 50, l = 10)  # Add space below plot
#   ) +
#   scale_x_discrete(
#     labels = c("CA", "CG", "GG", "GA")  # Custom order of conditions
#   ) +
#   guides(fill = "none", color = "none") +  # Remove redundant legends
#   # Add custom labels below the x-axis
#   annotate(
#     "text", x = 1.5, y = -2450, label = "Congruent", size = 5, hjust = 0.5, vjust = 1, fontface = "bold"
#   ) +
#   annotate(
#     "text", x = 3.5, y = -2450, label = "Incongruent", size = 5, hjust = 0.5, vjust = 1, fontface = "bold"
#   )
# 
# 
# 
# 
# library(ggplot2)
# library(grid)
# 
# 
# # Reorder levels of condition
# dwell.descr$condition <- factor(dwell.descr$condition, levels = c("CA", "CG", "GG", "GA"))
# 
# # Base ggplot
# p <- ggplot(data = dwell.descr, aes(x = condition, y = ia_dwell_time, fill = condition)) +
#   geom_boxplot(alpha = 0.3, color = "black") +  # Boxplots with lower transparency
#   geom_jitter(aes(color = condition),  # Jitter points with color by condition
#               position = position_jitterdodge(jitter.width = 0.4, dodge.width = 0.75), 
#               alpha = 0.6, shape = 21) +  # Points with less transparency
#   ylab("Dwell time (ms)") +
#   xlab("Condition") +  
#   #ylim(2500, 15000) +  
#   theme_bw() +
#   theme(
#     axis.text.x = element_text(size = 10),  # Keep axis labels unrotated
#     panel.grid.major.x = element_blank(),
#     axis.ticks.length = unit(0.5, "cm"),
#     plot.margin = margin(t = 10, r = 10, b = 60, l = 10)  # Add space below plot
#   ) +
#   scale_x_discrete(
#     labels = c("CA", "CG", "GG", "GA")  # Custom order of conditions
#   ) +
#   guides(fill = "none", color = "none")  # Remove redundant legends
# 
# # Print the ggplot and add grid text
# print(p)
# 
# # Add external labels
# grid.text("Congruent", x = 0.3, y = -1, gp = gpar(fontsize = 10, fontface = "bold"))
# grid.text("Incongruent", x = 0.7, y = -1, gp = gpar(fontsize = 10, fontface = "bold"))
# 
# p
```

* T-test comparing dwell times between object congruent and incongruent IAs
```{r}
test.IP.end.data.object.congruent.hand<-test.IP.end.data.object.congruent%>%
  filter(condition=="hand")

t.test(test.IP.end.data.object.congruent.hand$mean_dwell[test.IP.end.data.object.congruent.hand$object_congruent=="object_congruent_dwell_time"], test.IP.end.data.object.congruent.hand$mean_dwell[test.IP.end.data.object.congruent.hand$object_congruent=="object_incongruent_dwell_time"], paired=TRUE)
```


## Import data - reaction IP - 13200 ms 

```{r}
#IA report (from reaction IP - from frame 570 for Zserbo - session 1)
reaction.ip.orig.data.Zserbo <- read_delim("data/IA_report_IP_from_reaction_frame579.txt", na=".", delim="\t") %>% 
   filter(RECORDING_SESSION_LABEL=="Zserbo_1")

#IA report (from reaction IP - from frame 580 for all other sessions)
reaction.ip.orig.data <- read_delim("data/IA_report_IP_from_reaction.txt", na=".", delim="\t") %>% 
  filter(RECORDING_SESSION_LABEL!="Nala_2",
         RECORDING_SESSION_LABEL!="Sahibu_2",
         RECORDING_SESSION_LABEL!="Melody_1", #until here repeated due to dog leaving chinrest too early (before second agent's reaction)
         RECORDING_SESSION_LABEL!="Zserbo_1") %>% #excluded from here because frame 580 (the one defining the beginning of the reaction IP) was skipped in this video presentation, so we import this trial from frame 579 below
  rbind(reaction.ip.orig.data.Zserbo) %>% 
  arrange(RECORDING_SESSION_LABEL) #order rows alphabetically based on RECORDING_SESSION_LABEL
  levels(as.factor(reaction.ip.orig.data$IA_LABEL))

 
#full data file (IA report_IP_from reaction + demographics)
reaction.ip.data <- reaction.ip.orig.data %>%
  select(RECORDING_SESSION_LABEL, IP_LABEL, IA_LABEL,IA_ID, Trial_Index_, condition, trial_type, session_number, trial_number, video_file, DATA_FILE,  IA_AREA, IA_AVERAGE_FIX_PUPIL_SIZE,  IA_DWELL_TIME, "IA_DWELL_TIME_%", IA_FIXATION_COUNT, IA_MAX_FIX_PUPIL_SIZE, INTEREST_AREA_FIXATION_SEQUENCE, TRIAL_DWELL_TIME, TRIAL_FIXATION_COUNT, TRIAL_IA_COUNT, TRIAL_TOTAL_VISITED_IA_COUNT, IA_FIRST_FIXATION_TIME )%>%
  mutate(RECORDING_SESSION_LABEL=fct_recode(RECORDING_SESSION_LABEL, Georgia_1="Georgia1",Georgia_2="Georgia2", Georgia_3="Georgia3",Georgia_4="Georgia4", Mathilda_1="Mathild1", Mathilda_2="Mathild2", Mathilda_3="Mathild3", Mathilda_4="Mathild4" ))%>%
  separate(RECORDING_SESSION_LABEL, c("subject", "session.num"), sep = "_") %>% 
  full_join(demo.data)

#data checks
summary(reaction.ip.data$TRIAL_DWELL_TIME)
which(is.na(reaction.ip.data$TRIAL_DWELL_TIME)) #Knopf
levels(as.factor(reaction.ip.data$subject))
```

###Descriptive stats (reaction IP)

```{r}
#descriptive statistics

dwell.descr.react <-reaction.ip.data %>%
  filter(IA_LABEL!="FIXATION_TRIGGER") %>% 
  group_by(subject, trial_number, condition, trial_type, IA_LABEL, TRIAL_DWELL_TIME) %>% 
  summarise(ia_dwell_time=IA_DWELL_TIME) %>% 
   mutate(agent_type = ifelse(grepl("inviting|pointing", IA_LABEL), 
                             "communicating", 
                             "reacting")) %>% 
  mutate(proportion.dwell.time.agents=ia_dwell_time/TRIAL_DWELL_TIME) %>% 
  ungroup()

dwell.descr.aggr.react<-dwell.descr.react %>% 
  group_by(condition, trial_type) %>% 
  summarise(mean_dwell_time_to_agents=mean(ia_dwell_time),
            median_dwell_time=median(ia_dwell_time),
            mean_prop_dwell_agents=mean(proportion.dwell.time.agents, na.rm = TRUE),
            sd_dwell= sd(ia_dwell_time, na.rm = TRUE),
            se_dwell=sd(ia_dwell_time, na.rm = TRUE)/sqrt(length(ia_dwell_time)))

dwell.descr.part.react<-dwell.descr.react %>% 
  group_by(condition, subject) %>% 
  summarise(mean_dwell_time_to_agents=mean(ia_dwell_time, na.rm = TRUE),
            median_dwell_time=median(ia_dwell_time),
            mean_prop_dwell_agents=mean(proportion.dwell.time.agents, na.rm = TRUE),
            sd_dwell= sd(ia_dwell_time, na.rm = TRUE),
            se_dwell=sd(ia_dwell_time, na.rm = TRUE)/sqrt(length(ia_dwell_time)))
```
###Checking the data
```{r}
table(dwell.descr.part.react$condition, dwell.descr.part.react$subject) #Mailo misses 1 observation in CA (he will be tested again)
# dwell.descr.part<-dwell.descr.part %>% 
#   filter(subject!="Mailo")
```
###Plot dwell times as a function of trial type (based on aggregated data)

```{r}
#Version 1 (2 boxplots, one for congruent, one for incongruent conditions)
dwell.descr.aggr.react$trial_type<-fct_recode(dwell.descr.aggr.react$trial_type, "Congruent"="cong", "Incongruent"="incong")

ggplot(data = dwell.descr.aggr.react, aes(x = trial_type, y = mean_dwell_time_to_agents)) +
  geom_boxplot(alpha = 0.5) +  # Boxplot with transparency
  #geom_jitter(aes(fill = condition),  # Jitter points and color by condition
              # position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
              # alpha = 0.5, shape = 21) +  # Add transparency and shape
  ylab("Mean dwell time to agents") +
  xlab("Trial type") +
  ylim(3850, 4500) +  
  theme_bw()+
  stat_compare_means(paired = TRUE, method = "t.test", label.x= 1.4, label.y = 4500 )

t.test(dwell.descr.react$mean_dwell_time_to_agents[dwell.descr.react$condition=="CA"], dwell.descr.react$mean_dwell_time_to_agents[dwell.descr.react$condition=="CG"], paired=TRUE)
#LL:It seems there is no difference in the dwell times to the 2 agents combined. Next, do the same for the acting agent alone (or the 2 agents separately)
```
### Plot showing also condition, based on trial by trial data
```{r}
ggplot(data = dwell.descr.react, 
       aes(x = interaction(agent_type, trial_type, sep = "\n"), 
           y = ia_dwell_time)) +
  geom_boxplot(alpha = 0.5) +  # Boxplot with transparency
  # geom_jitter(aes(fill = condition),  # Uncomment to add jittered points colored by condition
  #             position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.75), 
  #             alpha = 0.5, shape = 21) +  # Add transparency and shape
  ylab("Mean dwell time to agents") +
  xlab("Agent Type\nTrial Type") +  # Label for clarity
  #ylim(3850, 4500) +  
  theme_bw()

```

###Preparing the data for analysis

```{r}
#bringing the data in the right format
model.data<-dwell.descr.react  %>%
  select(-IA_LABEL, -ia_dwell_time) %>% 
 pivot_wider(names_from=agent_type, values_from = proportion.dwell.time.agents) %>% 
  rename(prop.dwellt.communicating.agent=communicating, 
         prop.dwellt.reacting.agent=reacting)

summary(model.data$prop.dwellt.communicating.agent)
summary(model.data$prop.dwellt.reacting.agent)

#transforming DV to exclude 0 and 1s
model.data$prop.dwellt.communicating.agent.scaled <-
  (model.data$prop.dwellt.communicating.agent *
      (length(model.data$prop.dwellt.communicating.agent) - 1) + 0.5) / length(model.data$prop.dwellt.communicating.agent)

model.data$prop.dwellt.reacting.agent.scaled <-
  (model.data$prop.dwellt.reacting.agent *
      (length(model.data$prop.dwellt.reacting.agent) - 1) + 0.5) / length(model.data$prop.dwellt.reacting.agent)

summary(model.data$prop.dwellt.communicating.agent.scaled)
summary(model.data$prop.dwellt.reacting.agent.scaled)


model.data <- data.frame(model.data) %>%
  mutate(
    z.trial = as.numeric(scale(as.numeric(trial_number), center = TRUE, scale = TRUE)), #z-transform trial number
    condition.c = as.numeric(scale(as.numeric(as.factor(condition)), center = TRUE, scale = FALSE)),
    trial_type.c = as.numeric(scale(as.numeric(as.factor(trial_type)), center = TRUE, scale = FALSE))
  ) %>% #manually dummy code and center condition and trial_type for random effects part of the model
#the first as.numeric in this code is needed to drop the [,1] specification add would automatically add to the column names otherwise
  mutate(condition=as.factor(condition),
         trial_type=as.factor(trial_type)) #ensure condition and trial_type as treated as factors

hist(model.data$prop.dwellt.communicating.agent.scaled)
hist(model.data$prop.dwellt.reacting.agent.scaled)
```
### Descriptive stats 2 - separated by agents in the reaction IP

```{r}
dwell.descr.react.each.agent<-model.data %>% 
  group_by(condition, trial_type) %>% 
  summarise(mean_prop_dwell_time_communicating=mean(prop.dwellt.communicating.agent),
            mean_prop_dwell_time_reacting=mean(prop.dwellt.reacting.agent),
            sd_prop_dwell_comm=sd(prop.dwellt.communicating.agent, na.rm = TRUE),
            sd_prop_dwell_comm=sd(prop.dwellt.communicating.agent, na.rm = TRUE),
            median_dwell_timecomm=median(prop.dwellt.communicating.agent),
            median_dwell_time_react=median(prop.dwellt.reacting.agent),
            se_prop_dwell_comunicating=sd(prop.dwellt.communicating.agent, na.rm = TRUE)/sqrt(length(prop.dwellt.communicating.agent)),
            se_prop_dwell_reacting=sd(prop.dwellt.reacting.agent, na.rm = TRUE)/sqrt(length(prop.dwellt.reacting.agent)))
```

#### Beta GLMM -reaction IP

```{r}
#models for communicating agent (one with trial_type and one with condition as dv)
m1.reactIP.comm.trial.type<-glmmTMB(prop.dwellt.communicating.agent.scaled ~ trial_type + z.trial + (1+trial_type.c+z.trial||subject), family=beta_family, data=model.data,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))
#correlation between random effects excluded due to convergence issues

m2.reactIP.comm.cond<-glmmTMB(prop.dwellt.communicating.agent.scaled ~ condition + z.trial + (1+condition.c+z.trial||subject), family=beta_family, data=model.data,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))
#correlation between random effects excluded due to convergence issues

#models for reacting agent (one with trial_type and one with condition as dv)
m1.reactIP.react.trial.type<-glmmTMB(prop.dwellt.reacting.agent.scaled ~ trial_type + z.trial + (1+trial_type.c+z.trial||subject), family=beta_family, data=model.data,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))
#correlation between random effects excluded due to convergence issues

m2.reactIP.react.cond<-glmmTMB(prop.dwellt.reacting.agent.scaled ~ condition + z.trial + (1+condition.c+z.trial||subject), family=beta_family, data=model.data,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))
#correlation between random effects excluded due to convergence issues

#LL: missing: fit reduced models without condition to assess the significance of condition as a whole

#evaluate results
round(summary(m1.reactIP.comm.trial.type)$coefficients$cond,2)
round(summary(m2.reactIP.comm.cond)$coefficients$cond,2)
round(summary(m1.reactIP.react.trial.type)$coefficients$cond,2)
round(summary(m2.reactIP.react.cond)$coefficients$cond,2)#here something approaches significance

#LL: next, fit on the data in dwell.decr.react a beta model with interaction to check if dogs look longer to one of the agents or the other depending on the condition ia_dwell_time ~ condition (and/or trial_type)* agent_type
#The question would be if the approach/walking away or the come here/o away gesture are in themselves more interesting



```


```{r}
drop1_m1<-drop1(m1.endIP.largeIA, test="Chisq")
round(drop1_m1,3)
```

```{r}


m2.endIP.largeIA<-glmmTMB(prop.dwell.scaled ~ condition*target_location+z.trial +(1+condition.c+z.trial||subject), family=beta_family, data=model.data.end.IP.largerIA,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

```

```{r}
drop1_m2<-drop1(m2.endIP.largeIA, test="Chisq")
drop1_m2
```
##### assumptions
```{r}
#overdispersion
overdisp.test(m1.endIP.largeIA)

#distribution of the BLUPs
ranef.diagn.plot(m1.endIP.largeIA) 

#collinearity
xx=lme4::lmer(prop.dwell.scaled ~ condition + z.trial + condition_first +  target_location +
(1+condition.c+z.trial||subject),
data=model.data.end.IP.largerIA)
round(vif(xx), 3)
```

##### model stability beta model prop. dwell time
```{r}
m1.endIP.largeIA.stab=glmmTMB.stab(model.res=m1.endIP.largeIA, para=F, data=model.data.end.IP.largerIA)

#stability table
round(m1.endIP.largeIA.stab$summary[1:5, -1],2)
#stability plot
m.stab.plot(round(m1.endIP.largeIA.stab$summary[1:5, -1], 3))
```

##### confidence intervals beta model prop. dwell time
```{r}
boot.m1.endIP.largeIA=boot.glmmtmb(m=m1.endIP.largeIA, data=model.data.end.IP.largerIA,
discard.non.conv=F, nboots=1000, para=T, resol=100,
level=0.95, n.cores="all-1")

round(boot.m1.endIP.largeIA$ci.estimates$fe[1:5,],2)
```


The results of the dwell time analysis of the end IP show no difference between the hand or claw condition with respect to the looking times to the grasped object. Dogs showed a preference to look at the old identity object when this was in the upper location (evidenced by a significant target location effect).

### Intercept only model for proportion congruent object dwell time
```{r}
model.data.end.IP.largerIA$prop.dwell.scaled2 <-
  (
    model.data.end.IP.largerIA$proportion.object.congruent.dwell.time *
      (
        length(
          model.data.end.IP.largerIA$proportion.object.congruent.dwell.time
        ) - 1
      ) + 0.5
  ) / length(model.data.end.IP.largerIA$proportion.object.congruent.dwell.time)#transform DV to exclude 0 and 1s

m1.endIP.largeIA_interceptonly<-glmmTMB(prop.dwell.scaled2 ~  z.trial+(1+z.trial||subject), family=beta_family, data=model.data.end.IP.largerIA,  control=glmmTMBControl(optCtrl=list(iter.max=100000000, eval.max=100000000)))

round(summary(m1.endIP.largeIA_interceptonly)$coefficients$cond,3)
```

### First fixation analysis (binary)
```{r}
model.data.end.IP.first.looks<-end.ip.first.look%>%
  mutate(z.trial=scale(trial_within_block, center = TRUE, scale=TRUE),
         condition.c=scale(as.numeric(as.factor(condition)), center = TRUE, scale=FALSE))

summary(model.data.end.IP.first.looks)


m1.endIP.first_look<-glmer(object_congruent_first_look_noNA ~ condition + z.trial + condition_first+ target_location+(1+condition.c+z.trial|subject), family=binomial, data=model.data.end.IP.first.looks, control=glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000000)))

round(summary(m1.endIP.first_look)$coefficients,2)
```


```{r}
drop1_m1.first.look<-drop1(m1.endIP.first_look, test="Chisq")
round(drop1_m1.first.look,3)
```
####assumptions and stability
```{r}
#BLUPs
ranef.diagn.plot(m1.endIP.first_look)

#Stability
stab.m1.endIP.first_look=glmm.model.stab(model.res=m1.endIP.first_look,
contr=glmerControl(optimizer="bobyqa",
optCtrl=list(maxfun=10000)))

round(stab.m1.endIP.first_look$summary[1:5, -1],2)
m.stab.plot(stab.m1.endIP.first_look$summary[, -1])
```
####CIs binomial model first fixation
```{r}
boot.m1.endIP.first_look=boot.glmm.pred(model.res=m1.endIP.first_look,
nboots=1000, para=T, resol=1000, level=0.95,
use=NULL, n.cores="all-1")

first.fix.bin.cis<-round(boot.m1.endIP.first_look$ci.estimates, 2)
first.fix.bin.cis
```


### Intercept only model for first look
```{r}
m1.endIP.first_look_interceptonly<-glmer(object_congruent_first_look ~ 1+z.trial+(1+z.trial|subject), family=binomial, data=model.data.end.IP.first.looks, control=glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000000)))

round(summary(m1.endIP.first_look_interceptonly)$coefficients,3)
```

###First fixation to incongruent object (binary model)
```{r}
end.ip.first.look.incongr <- end.ip.data %>%
  select(
    subject,
    session.num,
    condition_trial,
    IP_LABEL,
    IA_LABEL,
    condition,
    condition_first,
    target,
    target_location,
    session,
    trial_within_block,
    video_file,
    video_latency,
    DATA_FILE,
    IA_FIRST_FIXATION_TIME
  ) %>%
  pivot_wider(names_from = IA_LABEL, values_from = IA_FIRST_FIXATION_TIME) %>%
  mutate(
    upper_IA_large = as.numeric(upper_IA_large),
    lower_IA_large = as.numeric(lower_IA_large)
  ) %>% 
 mutate(first_look = ifelse((
    upper_IA_large < lower_IA_large |
      (!is.na(upper_IA_large) & is.na(lower_IA_large))
  ), "upper", "NA")) %>%
  mutate(first_look2 = ifelse((
    lower_IA_large < upper_IA_large |
      (!is.na(lower_IA_large) & is.na(upper_IA_large))
  ), "lower", "NA")) %>% 

  mutate(first_look3=coalesce(first_look, first_look2)) %>% 
  mutate(object_incongruent_first_look = as.numeric(ifelse((target_location ==
                                                            "up" &
                                                            first_look3 == "lower"),
                                                         0,
                                                         ifelse((target_location == "down" &
                                                                   first_look3 == "upper"),
                                                                0,
                                                                ifelse((target_location == "up" &
                                                                          first_look3 == "upper"),
                                                                       1,
                                                                       ifelse((
                                                                         target_location == "down" & first_look3 == "lower"
                                                                       ), 1, NA)
                                                                )
                                                         )
  )),
  object_incongruent_first_look_noNA = as.numeric(ifelse(is.na(first_look3),0, object_incongruent_first_look )))

summary(end.ip.first.look.incongr$object_incongruent_first_look_noNA)

#manually replacing Nas that were not automatically scored correctly
end.ip.first.look.incongr[c(67,97),"object_incongruent_first_look_noNA"] <-0
 
summary(end.ip.first.look.incongr$object_incongruent_first_look_noNA)
```

```{r}
model.data.end.IP.first.look.incongr<-end.ip.first.look.incongr%>%
  mutate(z.trial=scale(trial_within_block, center = TRUE, scale=TRUE),
         condition.c=scale(as.numeric(as.factor(condition)), center = TRUE, scale=FALSE))

summary(model.data.end.IP.first.look.incongr)


m1.endIP.first_look.incongr<-glmer(object_incongruent_first_look_noNA ~ condition + z.trial + condition_first+ target_location+(1+condition.c+z.trial|subject), family=binomial, data=model.data.end.IP.first.look.incongr, control=glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 100000000)))

round(summary(m1.endIP.first_look.incongr)$coefficients,2)
```

```{r}
drop1_m1.first.look.incongr<-drop1(m1.endIP.first_look.incongr, test="Chisq")
round(drop1_m1.first.look.incongr,3)
```
####assumptions and stability first fix incongr obj
```{r}
#BLUPs
ranef.diagn.plot(m1.endIP.first_look.incongr)

#Stability
stab.m1.endIP.first_look.incongr=glmm.model.stab(model.res=m1.endIP.first_look.incongr,
contr=glmerControl(optimizer="bobyqa",
optCtrl=list(maxfun=10000)))

round(stab.m1.endIP.first_look.incongr$summary[1:5, -1],2)
m.stab.plot(stab.m1.endIP.first_look.incongr$summary[, -1])
```
####CIs binomial model first fixation incongr obj
```{r}
boot.m1.endIP.first_look.incongr=boot.glmm.pred(model.res=m1.endIP.first_look.incongr,
nboots=1000, para=T, resol=1000, level=0.95,
use=NULL, n.cores="all-1")

first.fix.incongr.bin.cis<-round(boot.m1.endIP.first_look.incongr$ci.estimates, 2)
first.fix.incongr.bin.cis
```